

# Stabilogram Diffusion Analysis R Script 
## Large Scale Study 'Posture Across the Lifespan'

### Loading Libraries
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(seewave)
library(segmented)
library(car)
library(tidyverse)

rm(list=ls())   #clear workspace
shell("cls")    #clear console


```



### Defining Vectors
```{r}
list <- list()
Rsquared_Short <- vector()
Fit_time_value <- vector()
Diff_Fast <- vector()
Rsquared_Long <- vector()
Diff_Slow <- vector()
STABILOGRAM_MUGGEO <- list()
X0_Value_Fast <- vector()
X0_Value_Slow <- vector()
Time_Crossover <- vector()
Result_Crossover <- vector()
list_Fitline_Long <- list()
list_Fitline_Short <- list()
list_my_Results <- list()

Hurst_Fast <- vector()
Hurst_Slow <- vector()
Rsquared_Short_H <- vector()
Rsquared_Long_H <- vector()
Cross_over_H <- vector()
list_Fitline_Long_H <- list()
list_Fitline_Short_H <- list()
list_my_Results_H <- list()
Time_Crossover_H <- vector()
Result_Crossover_H <- vector()
X0_Value_Fast_H <- vector()
X0_Value_Slow_H <- vector()
Fit_time_value_H <- vector()

```

# TOPIC 1: EYES CLOSED ANALYSIS 

### Setting Working Directory And Loading Lagged Distances

```{r warning=FALSE}
setwd("C:\\Research data\\Postural_Control_Github\\lagged_distances")
load("list_lagged_distances_EC_X.Rdata")
load("list_lagged_distances_EC_Y.Rdata")
load("list_lagged_distances_EC_R.Rdata")
```


# PART 1: DIFFUSION PARAMETERS

## Fit Time By Function "segmented" ~ Muggeo

```{r}
for(i in 1:301){

STABILOGRAM_MUGGEO[[i]] <- list_lagged_distances_EC_R[[i]][1:3000,] 

fit.glm <- glm(results~time, data=STABILOGRAM_MUGGEO[[i]], family=quasi)
  
fit.seg <- segmented(fit.glm, seg.Z = ~time, psi=list(time=c(800)))

Fit_time_value[i] <- summary(fit.seg)$psi[2]
}

names <- names(list_lagged_distances_EC_R)


summary(Fit_time_value)

```

## Calculation of Fast Diffusion component

```{r}
  for(i in 1:301){
  linear_dataset <- list_lagged_distances_EC_R[[i]][50:Fit_time_value[i],] 
  Squared_distance_Short <- linear_dataset$results
  mod <- lm(linear_dataset$results~linear_dataset$time)
  
  Diff_Fast[i] <- mod$coefficients[2] #slope
  X0_Value_Fast[i] <- mod$coefficients[1] #Value for x=0
  
  summary <- summary(mod)
  
  Rsquared_Short[i] <- summary$r.squared
  Fitvalue_Short <- mod$fitted.values
  Time_fitline <- 50:Fit_time_value[i]
  
  Fitline_Short <- cbind(Time_fitline, Fitvalue_Short)
  Fitline_Short <- as.data.frame(Fitline_Short)
  
  list_Fitline_Short[[i]] <- Fitline_Short
  
  #df <- as.data.frame(cbind(Time_fitline, Fitvalue_Short, Squared_distance_Short))
  #PRINT <- df%>%
  #  ggplot(aes(x=Time_fitline, y=Squared_distance_Short)) +
  #  geom_line()+
  #  geom_line(y=Fitvalue_Short)
  #print(PRINT)
  }
summary(Rsquared_Short)


```


## Calculation of Slow Diffusion component
```{r}
  for(i in 1:301){
  linear_dataset <- list_lagged_distances_EC_R[[i]][Fit_time_value[i]:10000,] 
  Squared_distance_long <- linear_dataset$results
  mod <- lm(linear_dataset$results~linear_dataset$time)
  
  X0_Value_Slow[i] <- mod$coefficients[1] #Value for x=0
  Diff_Slow[i] <- mod$coefficients[2]
  summary <- summary(mod)
  
  Rsquared_Long[i] <- summary$r.squared
  Fitvalue_Long <- mod$fitted.values
  Time_fitline <- Fit_time_value[i]:10000
  
  Fitline_Long <- cbind(Time_fitline, Fitvalue_Long)
  Fitline_Long <- as.data.frame(Fitline_Long)
  
  list_Fitline_Long[[i]] <- Fitline_Long
  
  #df <- as.data.frame(cbind(Time_fitline, Fitvalue_Long, Squared_distance_long))
  #PRINT <- df%>%
  #  ggplot(aes(x=Time_fitline, y=Squared_distance_long)) +
  #  geom_line()+
  #  geom_line(y=Fitvalue_Long)
  #print(PRINT)
  }
summary(Rsquared_Long)

```

## Calculation Of Cross Over

```{r}
for(i in 1:301){
mycoeffmatrix <- matrix(c(-Diff_Fast[i], 1, -Diff_Slow[i], 1), nrow=2, ncol = 2, byrow=TRUE)
myRhsMatrix <- matrix(c(X0_Value_Fast[i], X0_Value_Slow[i]), nrow=2, ncol = 1, byrow=TRUE)
myInverse <- solve(mycoeffmatrix)
myResult <- myInverse%*%myRhsMatrix

Time_Crossover[i] <- myResult[1,1]
Result_Crossover[i] <- myResult[2,1]

list_my_Results[[i]] <- myResult

}

summary(Time_Crossover)

```




# Final Diffusion Plot 

```{r}
#Determining the GG lines to connect the linear regressions with the crossover (to check visually)

for(i in 1:20){
  
myResult <- list_my_Results[[i]]
Fitline_Long <- list_Fitline_Long[[i]]
Fitline_Short <- list_Fitline_Short[[i]]
X <- Fitline_Long[1,1]
Y <- Fitline_Long[1,2]
vector1_LONG <- c(X,Y)
vector2 <- myResult[,1]

GG_LINE_LONG <- as.data.frame(rbind(vector1_LONG, vector2))


X <- Fitline_Short[1,1]
Y <- Fitline_Short[1,2]
vector1_SHORT<- c(X,Y)

GG_LINE_SHORT <- as.data.frame(rbind(vector1_SHORT, vector2))

#Plotting 

colnames(Fitline_Short) <- c("Time_fitline", "Fitvalue")
colnames(Fitline_Long) <- c("Time_fitline", "Fitvalue")
  TOTAL_FIT <- rbind(Fitline_Short, Fitline_Long)
  

  again <- list_lagged_distances_EC_R[[i]][50:10000,]
  
  again <- cbind(again, TOTAL_FIT$Fitvalue)

  wow <- again%>%
    ggplot(aes(x=time, y=results)) +
    geom_line()+
    geom_line(data=Fitline_Long, aes(Time_fitline, Fitvalue))+
    geom_line(data=Fitline_Short, aes(Time_fitline, Fitvalue))+
    ggtitle(names[i])+
    geom_point(aes(x=Time_Crossover[i], Result_Crossover[i]), colour="blue", size=4)+
    geom_line(data=GG_LINE_LONG, aes(V1, V2), linetype = "longdash")+
    geom_line(data=GG_LINE_SHORT, aes(V1, V2), linetype = "longdash")
  print(wow)
}
```



# PART 2: EC X HURST PARAMETERS OF ALL TRIALS




## Fit Time By Function "segmented" ~ Muggeo

```{r}
for(i in 1:301){

STABILOGRAM_MUGGEO[[i]] <- list_lagged_distances_EC_R[[i]][1:3000,] #skip de eerste 5 ms


STABILOGRAM_MUGGEO[[i]]$time <- log10(STABILOGRAM_MUGGEO[[i]]$time)
STABILOGRAM_MUGGEO[[i]]$results <- log10(STABILOGRAM_MUGGEO[[i]]$results)

fit.glm <- glm(results~time, data=STABILOGRAM_MUGGEO[[i]], family=quasi)
  
fit.seg <- segmented(fit.glm, seg.Z = ~time, psi=list(time=c(2.9)))

Fit_time_value_H[i] <- summary(fit.seg)$psi[2]
}



summary(10^Fit_time_value_H)

```



## Calculation of Fast Hurst component

```{r}

  for(i in 1:301){
  
  linear_dataset <- list_lagged_distances_EC_R[[i]]
  linear_dataset$time <- log10(linear_dataset$time)
  linear_dataset$results <- log10(linear_dataset$results)
  
  linear_dataset <- linear_dataset[1:(10^Fit_time_value_H[i]),]
  
  
  
  Squared_distance_Short <- linear_dataset$results
  mod <- lm(linear_dataset$results~linear_dataset$time)
  
  #### TOT HIER KLOPT HET!! 
  
  Hurst_Fast[i] <- mod$coefficients[2] #slope
  X0_Value_Fast_H[i] <- mod$coefficients[1] #Value for x=0
  
  summary <- summary(mod)
  
  Rsquared_Short_H[i] <- summary$r.squared
  Fitvalue_Short <- mod$fitted.values
  
  Time_fitline <- linear_dataset$time
  
  
  Fitline_Short <- cbind(Time_fitline, Fitvalue_Short)
  Fitline_Short <- as.data.frame(Fitline_Short)
  
  list_Fitline_Short_H[[i]] <- Fitline_Short
  
  #df <- as.data.frame(cbind(Time_fitline, Fitvalue_Short, Squared_distance_Short))
  #PRINT <- df%>%
  #ggplot(aes(x=Time_fitline, y=Squared_distance_Short)) +
  #  geom_line()+
  #  geom_line(y=Fitvalue_Short)
  #print(PRINT)
  
  }
summary(Rsquared_Short_H)

summary(Hurst_Fast)


```


## Calculation of Slow Hurst component
```{r}

  for(i in 1:301){
    
  linear_dataset <- list_lagged_distances_EC_R[[i]]
  linear_dataset$time <- log10(linear_dataset$time)
  linear_dataset$results <- log10(linear_dataset$results)
  nrow(linear_dataset)
  linear_dataset <- linear_dataset[(10^Fit_time_value_H[i]):10000,]
  
  Squared_distance_long <- linear_dataset$results
  mod <- lm(linear_dataset$results~linear_dataset$time)
  
  
  X0_Value_Slow_H[i] <- mod$coefficients[1] #Value for x=0
  Hurst_Slow[i] <- mod$coefficients[2]
  
  summary <- summary(mod)
  
  Rsquared_Long_H[i] <- summary$r.squared
  Fitvalue_Long <- mod$fitted.values
  
  Time_fitline <- linear_dataset$time
  
  Fitline_Long <- cbind(Time_fitline, Fitvalue_Long)
  Fitline_Long <- as.data.frame(Fitline_Long)
  
  list_Fitline_Long_H[[i]] <- Fitline_Long
  
  #df <- as.data.frame(cbind(Time_fitline, Fitvalue_Long, Squared_distance_long))
  #PRINT <- df%>%
  #  ggplot(aes(x=Time_fitline, y=Squared_distance_long)) +
  #  geom_line()+
  #  geom_line(y=Fitvalue_Long)
  #print(PRINT)
  }
summary(Rsquared_Long_H)

summary(Hurst_Fast)

```


## Calculation Of Cross Over

```{r}
for(i in 1:301){
mycoeffmatrix <- matrix(c(-Hurst_Fast[i], 1, -Hurst_Slow[i], 1), nrow=2, ncol = 2, byrow=TRUE)
myRhsMatrix <- matrix(c(X0_Value_Fast_H[i], X0_Value_Slow_H[i]), nrow=2, ncol = 1, byrow=TRUE)
myInverse <- solve(mycoeffmatrix)
myResult <- myInverse%*%myRhsMatrix

Time_Crossover_H[i] <- myResult[1,1]
Result_Crossover_H[i] <- myResult[2,1]

list_my_Results_H[[i]] <- myResult

}

summary(Time_Crossover_H)

```


# EC X SAVE


## Data wrangling


```{r message=FALSE, warning=FALSE}
Subj <- as.numeric(names)

stabilogram_EC_R <- cbind.data.frame(Subj, Diff_Fast, Diff_Slow, Time_Crossover, Fit_time_value, Hurst_Fast, Hurst_Slow, Time_Crossover_H, Fit_time_value_H, Result_Crossover)

colnames(stabilogram_EC_R) <- c("Subj", "d_s", "d_l", "d_cx", "d_segm", "h_s", "h_l", "h_cx", "h_segm", "d_cy")

options("scipen"=100, "digits"=4)

stabilogram_EC_R <- pivot_longer(stabilogram_EC_R, cols=c("d_s", "d_l", "d_cx", "d_segm", "h_s", "h_l", "h_cx", "h_segm", "d_cy"), names_to = "Param")


```




#################################





### Defining Vectors
```{r}
list <- list()
Rsquared_Short <- vector()
Fit_time_value <- vector()
Diff_Fast <- vector()
Rsquared_Long <- vector()
Diff_Slow <- vector()
STABILOGRAM_MUGGEO <- list()
X0_Value_Fast <- vector()
X0_Value_Slow <- vector()
Time_Crossover <- vector()
Result_Crossover <- vector()
list_Fitline_Long <- list()
list_Fitline_Short <- list()
list_my_Results <- list()

Hurst_Fast <- vector()
Hurst_Slow <- vector()
Rsquared_Short_H <- vector()
Rsquared_Long_H <- vector()
Cross_over_H <- vector()
list_Fitline_Long_H <- list()
list_Fitline_Short_H <- list()
list_my_Results_H <- list()
Time_Crossover_H <- vector()
Result_Crossover_H <- vector()
X0_Value_Fast_H <- vector()
X0_Value_Slow_H <- vector()
Fit_time_value_H <- vector()

```

# TOPIC 1: EYES CLOSED ANALYSIS 

### Setting Working Directory And Loading Lagged Distances

```{r warning=FALSE}
setwd("C:\\Research data\\Postural_Control_Github\\lagged_distances")
load("list_lagged_distances_TR_X.Rdata")
load("list_lagged_distances_TR_Y.Rdata")
load("list_lagged_distances_TR_R.Rdata")
```


# PART 1: DIFFUSION PARAMETERS

## Fit Time By Function "segmented" ~ Muggeo

```{r}
for(i in 1:301){

STABILOGRAM_MUGGEO[[i]] <- list_lagged_distances_TR_R[[i]][1:3000,] 

fit.glm <- glm(results~time, data=STABILOGRAM_MUGGEO[[i]], family=quasi)
  
fit.seg <- segmented(fit.glm, seg.Z = ~time, psi=list(time=c(800)))

Fit_time_value[i] <- summary(fit.seg)$psi[2]
}

names <- names(list_lagged_distances_TR_R)


summary(Fit_time_value)

```

## Calculation of Fast Diffusion component

```{r}
  for(i in 1:301){
  linear_dataset <- list_lagged_distances_TR_R[[i]][50:Fit_time_value[i],] 
  Squared_distance_Short <- linear_dataset$results
  mod <- lm(linear_dataset$results~linear_dataset$time)
  
  Diff_Fast[i] <- mod$coefficients[2] #slope
  X0_Value_Fast[i] <- mod$coefficients[1] #Value for x=0
  
  summary <- summary(mod)
  
  Rsquared_Short[i] <- summary$r.squared
  Fitvalue_Short <- mod$fitted.values
  Time_fitline <- 50:Fit_time_value[i]
  
  Fitline_Short <- cbind(Time_fitline, Fitvalue_Short)
  Fitline_Short <- as.data.frame(Fitline_Short)
  
  list_Fitline_Short[[i]] <- Fitline_Short
  
  #df <- as.data.frame(cbind(Time_fitline, Fitvalue_Short, Squared_distance_Short))
  #PRINT <- df%>%
  #  ggplot(aes(x=Time_fitline, y=Squared_distance_Short)) +
  #  geom_line()+
  #  geom_line(y=Fitvalue_Short)
  #print(PRINT)
  }
summary(Rsquared_Short)


```


## Calculation of Slow Diffusion component
```{r}
  for(i in 1:301){
  linear_dataset <- list_lagged_distances_TR_R[[i]][Fit_time_value[i]:10000,] 
  Squared_distance_long <- linear_dataset$results
  mod <- lm(linear_dataset$results~linear_dataset$time)
  
  X0_Value_Slow[i] <- mod$coefficients[1] #Value for x=0
  Diff_Slow[i] <- mod$coefficients[2]
  summary <- summary(mod)
  
  Rsquared_Long[i] <- summary$r.squared
  Fitvalue_Long <- mod$fitted.values
  Time_fitline <- Fit_time_value[i]:10000
  
  Fitline_Long <- cbind(Time_fitline, Fitvalue_Long)
  Fitline_Long <- as.data.frame(Fitline_Long)
  
  list_Fitline_Long[[i]] <- Fitline_Long
  
  #df <- as.data.frame(cbind(Time_fitline, Fitvalue_Long, Squared_distance_long))
  #PRINT <- df%>%
  #  ggplot(aes(x=Time_fitline, y=Squared_distance_long)) +
  #  geom_line()+
  #  geom_line(y=Fitvalue_Long)
  #print(PRINT)
  }
summary(Rsquared_Long)

```

## Calculation Of Cross Over

```{r}
for(i in 1:301){
mycoeffmatrix <- matrix(c(-Diff_Fast[i], 1, -Diff_Slow[i], 1), nrow=2, ncol = 2, byrow=TRUE)
myRhsMatrix <- matrix(c(X0_Value_Fast[i], X0_Value_Slow[i]), nrow=2, ncol = 1, byrow=TRUE)
myInverse <- solve(mycoeffmatrix)
myResult <- myInverse%*%myRhsMatrix

Time_Crossover[i] <- myResult[1,1]
Result_Crossover[i] <- myResult[2,1]

list_my_Results[[i]] <- myResult

}

summary(Time_Crossover)

```




# Final Diffusion Plot 

```{r}
#Determining the GG lines to connect the linear regressions with the crossover (to check visually)

for(i in 1:20){
  
myResult <- list_my_Results[[i]]
Fitline_Long <- list_Fitline_Long[[i]]
Fitline_Short <- list_Fitline_Short[[i]]
X <- Fitline_Long[1,1]
Y <- Fitline_Long[1,2]
vector1_LONG <- c(X,Y)
vector2 <- myResult[,1]

GG_LINE_LONG <- as.data.frame(rbind(vector1_LONG, vector2))


X <- Fitline_Short[1,1]
Y <- Fitline_Short[1,2]
vector1_SHORT<- c(X,Y)

GG_LINE_SHORT <- as.data.frame(rbind(vector1_SHORT, vector2))

#Plotting 

colnames(Fitline_Short) <- c("Time_fitline", "Fitvalue")
colnames(Fitline_Long) <- c("Time_fitline", "Fitvalue")
  TOTAL_FIT <- rbind(Fitline_Short, Fitline_Long)
  

  again <- list_lagged_distances_TR_R[[i]][50:10000,]
  
  again <- cbind(again, TOTAL_FIT$Fitvalue)

  wow <- again%>%
    ggplot(aes(x=time, y=results)) +
    geom_line()+
    geom_line(data=Fitline_Long, aes(Time_fitline, Fitvalue))+
    geom_line(data=Fitline_Short, aes(Time_fitline, Fitvalue))+
    ggtitle(names[i])+
    geom_point(aes(x=Time_Crossover[i], Result_Crossover[i]), colour="blue", size=4)+
    geom_line(data=GG_LINE_LONG, aes(V1, V2), linetype = "longdash")+
    geom_line(data=GG_LINE_SHORT, aes(V1, V2), linetype = "longdash")
  print(wow)
}
```



# PART 2: TR X HURST PARAMETERS OF ALL TRIALS




## Fit Time By Function "segmented" ~ Muggeo

```{r}
for(i in 1:301){

STABILOGRAM_MUGGEO[[i]] <- list_lagged_distances_TR_R[[i]][1:3000,] #skip de eerste 5 ms


STABILOGRAM_MUGGEO[[i]]$time <- log10(STABILOGRAM_MUGGEO[[i]]$time)
STABILOGRAM_MUGGEO[[i]]$results <- log10(STABILOGRAM_MUGGEO[[i]]$results)

fit.glm <- glm(results~time, data=STABILOGRAM_MUGGEO[[i]], family=quasi)
  
fit.seg <- segmented(fit.glm, seg.Z = ~time, psi=list(time=c(2.9)))

Fit_time_value_H[i] <- summary(fit.seg)$psi[2]
}



summary(10^Fit_time_value_H)

```



## Calculation of Fast Hurst component

```{r}

  for(i in 1:301){
  
  linear_dataset <- list_lagged_distances_TR_R[[i]]
  linear_dataset$time <- log10(linear_dataset$time)
  linear_dataset$results <- log10(linear_dataset$results)
  
  linear_dataset <- linear_dataset[1:(10^Fit_time_value_H[i]),]
  
  
  
  Squared_distance_Short <- linear_dataset$results
  mod <- lm(linear_dataset$results~linear_dataset$time)
  
  #### TOT HIER KLOPT HET!! 
  
  Hurst_Fast[i] <- mod$coefficients[2] #slope
  X0_Value_Fast_H[i] <- mod$coefficients[1] #Value for x=0
  
  summary <- summary(mod)
  
  Rsquared_Short_H[i] <- summary$r.squared
  Fitvalue_Short <- mod$fitted.values
  
  Time_fitline <- linear_dataset$time
  
  
  Fitline_Short <- cbind(Time_fitline, Fitvalue_Short)
  Fitline_Short <- as.data.frame(Fitline_Short)
  
  list_Fitline_Short_H[[i]] <- Fitline_Short
  
  #df <- as.data.frame(cbind(Time_fitline, Fitvalue_Short, Squared_distance_Short))
  #PRINT <- df%>%
  #ggplot(aes(x=Time_fitline, y=Squared_distance_Short)) +
  #  geom_line()+
  #  geom_line(y=Fitvalue_Short)
  #print(PRINT)
  
  }
summary(Rsquared_Short_H)

summary(Hurst_Fast)


```


## Calculation of Slow Hurst component
```{r}

  for(i in 1:301){
    
  linear_dataset <- list_lagged_distances_TR_R[[i]]
  linear_dataset$time <- log10(linear_dataset$time)
  linear_dataset$results <- log10(linear_dataset$results)
  nrow(linear_dataset)
  linear_dataset <- linear_dataset[(10^Fit_time_value_H[i]):10000,]
  
  Squared_distance_long <- linear_dataset$results
  mod <- lm(linear_dataset$results~linear_dataset$time)
  
  
  X0_Value_Slow_H[i] <- mod$coefficients[1] #Value for x=0
  Hurst_Slow[i] <- mod$coefficients[2]
  
  summary <- summary(mod)
  
  Rsquared_Long_H[i] <- summary$r.squared
  Fitvalue_Long <- mod$fitted.values
  
  Time_fitline <- linear_dataset$time
  
  Fitline_Long <- cbind(Time_fitline, Fitvalue_Long)
  Fitline_Long <- as.data.frame(Fitline_Long)
  
  list_Fitline_Long_H[[i]] <- Fitline_Long
  
  #df <- as.data.frame(cbind(Time_fitline, Fitvalue_Long, Squared_distance_long))
  #PRINT <- df%>%
  #  ggplot(aes(x=Time_fitline, y=Squared_distance_long)) +
  #  geom_line()+
  #  geom_line(y=Fitvalue_Long)
  #print(PRINT)
  }
summary(Rsquared_Long_H)

summary(Hurst_Fast)

```


## Calculation Of Cross Over

```{r}
for(i in 1:301){
mycoeffmatrix <- matrix(c(-Hurst_Fast[i], 1, -Hurst_Slow[i], 1), nrow=2, ncol = 2, byrow=TRUE)
myRhsMatrix <- matrix(c(X0_Value_Fast_H[i], X0_Value_Slow_H[i]), nrow=2, ncol = 1, byrow=TRUE)
myInverse <- solve(mycoeffmatrix)
myResult <- myInverse%*%myRhsMatrix

Time_Crossover_H[i] <- myResult[1,1]
Result_Crossover_H[i] <- myResult[2,1]

list_my_Results_H[[i]] <- myResult

}

summary(Time_Crossover_H)

```


# TR X SAVE


## Data wrangling


```{r message=FALSE, warning=FALSE}
Subj <- as.numeric(names)

stabilogram_TR_R <- cbind.data.frame(Subj, Diff_Fast, Diff_Slow, Time_Crossover, Fit_time_value, Hurst_Fast, Hurst_Slow, Time_Crossover_H, Fit_time_value_H, Result_Crossover)

colnames(stabilogram_TR_R) <- c("Subj", "d_s", "d_l", "d_cx", "d_segm", "h_s", "h_l", "h_cx", "h_segm", "d_cy")

options("scipen"=100, "digits"=4)

stabilogram_TR_R <- pivot_longer(stabilogram_TR_R, cols=c("d_s", "d_l", "d_cx", "d_segm", "h_s", "h_l", "h_cx", "h_segm", "d_cy"), names_to = "Param")



```






#################################





### Defining Vectors
```{r}
list <- list()
Rsquared_Short <- vector()
Fit_time_value <- vector()
Diff_Fast <- vector()
Rsquared_Long <- vector()
Diff_Slow <- vector()
STABILOGRAM_MUGGEO <- list()
X0_Value_Fast <- vector()
X0_Value_Slow <- vector()
Time_Crossover <- vector()
Result_Crossover <- vector()
list_Fitline_Long <- list()
list_Fitline_Short <- list()
list_my_Results <- list()

Hurst_Fast <- vector()
Hurst_Slow <- vector()
Rsquared_Short_H <- vector()
Rsquared_Long_H <- vector()
Cross_over_H <- vector()
list_Fitline_Long_H <- list()
list_Fitline_Short_H <- list()
list_my_Results_H <- list()
Time_Crossover_H <- vector()
Result_Crossover_H <- vector()
X0_Value_Fast_H <- vector()
X0_Value_Slow_H <- vector()
Fit_time_value_H <- vector()

```

# TOPIC 1: EO ANALYSIS 

### Setting Working Directory And Loading Lagged Distances

```{r warning=FALSE}
setwd("C:\\Research data\\Postural_Control_Github\\lagged_distances")
load("list_lagged_distances_EO_X.Rdata")
load("list_lagged_distances_EO_Y.Rdata")
load("list_lagged_distances_EO_R.Rdata")
```


# PART 1: DIFFUSION PARAMETERS

## Fit Time By Function "segmented" ~ Muggeo

```{r}
for(i in 1:1204){

STABILOGRAM_MUGGEO[[i]] <- list_lagged_distances_EO_R[[i]][1:3000,] 

fit.glm <- glm(results~time, data=STABILOGRAM_MUGGEO[[i]], family=quasi)
  
fit.seg <- segmented(fit.glm, seg.Z = ~time, psi=list(time=c(800)))

Fit_time_value[i] <- summary(fit.seg)$psi[2]
}



# Keeping only the first part of the name which is equivalent to their subject ID ("names_1")
names <- names(list_lagged_distances_EO_R)


names_split <- strsplit(names, split='_', fixed=TRUE)

names_1 <- vector()
trial <- vector()

for(i in 1:1204){
names_1[i] <- names_split[[i]][1]
trial[i] <- names_split[[i]][2]

}



# Summary of the breakpoint values ("Fit_time_value[i]")
summary(Fit_time_value)


```

## Calculation of Fast Diffusion component

```{r}
  for(i in 1:1204){
  linear_dataset <- list_lagged_distances_EO_R[[i]][50:Fit_time_value[i],] 
  Squared_distance_Short <- linear_dataset$results
  mod <- lm(linear_dataset$results~linear_dataset$time)
  
  Diff_Fast[i] <- mod$coefficients[2] #slope
  X0_Value_Fast[i] <- mod$coefficients[1] #Value for x=0
  
  summary <- summary(mod)
  
  Rsquared_Short[i] <- summary$r.squared
  Fitvalue_Short <- mod$fitted.values
  Time_fitline <- 50:Fit_time_value[i]
  
  Fitline_Short <- cbind(Time_fitline, Fitvalue_Short)
  Fitline_Short <- as.data.frame(Fitline_Short)
  
  list_Fitline_Short[[i]] <- Fitline_Short
  
  #df <- as.data.frame(cbind(Time_fitline, Fitvalue_Short, Squared_distance_Short))
  #PRINT <- df%>%
  #  ggplot(aes(x=Time_fitline, y=Squared_distance_Short)) +
  #  geom_line()+
  #  geom_line(y=Fitvalue_Short)
  #print(PRINT)
  }
summary(Rsquared_Short)


```


## Calculation of Slow Diffusion component
```{r}
  for(i in 1:1204){
  linear_dataset <- list_lagged_distances_EO_R[[i]][Fit_time_value[i]:10000,] 
  Squared_distance_long <- linear_dataset$results
  mod <- lm(linear_dataset$results~linear_dataset$time)
  
  X0_Value_Slow[i] <- mod$coefficients[1] #Value for x=0
  Diff_Slow[i] <- mod$coefficients[2]
  summary <- summary(mod)
  
  Rsquared_Long[i] <- summary$r.squared
  Fitvalue_Long <- mod$fitted.values
  Time_fitline <- Fit_time_value[i]:10000
  
  Fitline_Long <- cbind(Time_fitline, Fitvalue_Long)
  Fitline_Long <- as.data.frame(Fitline_Long)
  
  list_Fitline_Long[[i]] <- Fitline_Long
  
  #df <- as.data.frame(cbind(Time_fitline, Fitvalue_Long, Squared_distance_long))
  #PRINT <- df%>%
  #  ggplot(aes(x=Time_fitline, y=Squared_distance_long)) +
  #  geom_line()+
  #  geom_line(y=Fitvalue_Long)
  #print(PRINT)
  }
summary(Rsquared_Long)

```

## Calculation Of Cross Over

```{r}
for(i in 1:1204){
mycoeffmatrix <- matrix(c(-Diff_Fast[i], 1, -Diff_Slow[i], 1), nrow=2, ncol = 2, byrow=TRUE)
myRhsMatrix <- matrix(c(X0_Value_Fast[i], X0_Value_Slow[i]), nrow=2, ncol = 1, byrow=TRUE)
myInverse <- solve(mycoeffmatrix)
myResult <- myInverse%*%myRhsMatrix

Time_Crossover[i] <- myResult[1,1]
Result_Crossover[i] <- myResult[2,1]

list_my_Results[[i]] <- myResult

}

summary(Time_Crossover)

```




# Final Diffusion Plot 

```{r}
#Determining the GG lines to connect the linear regressions with the crossover (to check visually)

for(i in 1:20){
  
myResult <- list_my_Results[[i]]
Fitline_Long <- list_Fitline_Long[[i]]
Fitline_Short <- list_Fitline_Short[[i]]
X <- Fitline_Long[1,1]
Y <- Fitline_Long[1,2]
vector1_LONG <- c(X,Y)
vector2 <- myResult[,1]

GG_LINE_LONG <- as.data.frame(rbind(vector1_LONG, vector2))


X <- Fitline_Short[1,1]
Y <- Fitline_Short[1,2]
vector1_SHORT<- c(X,Y)

GG_LINE_SHORT <- as.data.frame(rbind(vector1_SHORT, vector2))

#Plotting 

colnames(Fitline_Short) <- c("Time_fitline", "Fitvalue")
colnames(Fitline_Long) <- c("Time_fitline", "Fitvalue")
  TOTAL_FIT <- rbind(Fitline_Short, Fitline_Long)
  

  again <- list_lagged_distances_EO_R[[i]][50:10000,]
  
  again <- cbind(again, TOTAL_FIT$Fitvalue)

  wow <- again%>%
    ggplot(aes(x=time, y=results)) +
    geom_line()+
    geom_line(data=Fitline_Long, aes(Time_fitline, Fitvalue))+
    geom_line(data=Fitline_Short, aes(Time_fitline, Fitvalue))+
    ggtitle(names[i])+
    geom_point(aes(x=Time_Crossover[i], Result_Crossover[i]), colour="blue", size=4)+
    geom_line(data=GG_LINE_LONG, aes(V1, V2), linetype = "longdash")+
    geom_line(data=GG_LINE_SHORT, aes(V1, V2), linetype = "longdash")
  print(wow)
}
```



# PART 2: EO X HURST PARAMETERS OF ALL TRIALS




## Fit Time By Function "segmented" ~ Muggeo

```{r}
for(i in 1:1204){

STABILOGRAM_MUGGEO[[i]] <- list_lagged_distances_EO_R[[i]][1:3000,] #skip de eerste 5 ms


STABILOGRAM_MUGGEO[[i]]$time <- log10(STABILOGRAM_MUGGEO[[i]]$time)
STABILOGRAM_MUGGEO[[i]]$results <- log10(STABILOGRAM_MUGGEO[[i]]$results)

fit.glm <- glm(results~time, data=STABILOGRAM_MUGGEO[[i]], family=quasi)
  
fit.seg <- segmented(fit.glm, seg.Z = ~time, psi=list(time=c(2.9)))

Fit_time_value_H[i] <- summary(fit.seg)$psi[2]
}



summary(10^Fit_time_value_H)

```



## Calculation of Fast Hurst component

```{r}

  for(i in 1:1204){
  
  linear_dataset <- list_lagged_distances_EO_R[[i]]
  linear_dataset$time <- log10(linear_dataset$time)
  linear_dataset$results <- log10(linear_dataset$results)
  
  linear_dataset <- linear_dataset[1:(10^Fit_time_value_H[i]),]
  
  
  
  Squared_distance_Short <- linear_dataset$results
  mod <- lm(linear_dataset$results~linear_dataset$time)
  
  #### TOT HIER KLOPT HET!! 
  
  Hurst_Fast[i] <- mod$coefficients[2] #slope
  X0_Value_Fast_H[i] <- mod$coefficients[1] #Value for x=0
  
  summary <- summary(mod)
  
  Rsquared_Short_H[i] <- summary$r.squared
  Fitvalue_Short <- mod$fitted.values
  
  Time_fitline <- linear_dataset$time
  
  
  Fitline_Short <- cbind(Time_fitline, Fitvalue_Short)
  Fitline_Short <- as.data.frame(Fitline_Short)
  
  list_Fitline_Short_H[[i]] <- Fitline_Short
  
  #df <- as.data.frame(cbind(Time_fitline, Fitvalue_Short, Squared_distance_Short))
  #PRINT <- df%>%
  #ggplot(aes(x=Time_fitline, y=Squared_distance_Short)) +
  #  geom_line()+
  #  geom_line(y=Fitvalue_Short)
  #print(PRINT)
  
  }
summary(Rsquared_Short_H)

summary(Hurst_Fast)


```


## Calculation of Slow Hurst component
```{r}

  for(i in 1:1204){
    
  linear_dataset <- list_lagged_distances_EO_R[[i]]
  linear_dataset$time <- log10(linear_dataset$time)
  linear_dataset$results <- log10(linear_dataset$results)
  nrow(linear_dataset)
  linear_dataset <- linear_dataset[(10^Fit_time_value_H[i]):10000,]
  
  Squared_distance_long <- linear_dataset$results
  mod <- lm(linear_dataset$results~linear_dataset$time)
  
  
  X0_Value_Slow_H[i] <- mod$coefficients[1] #Value for x=0
  Hurst_Slow[i] <- mod$coefficients[2]
  
  summary <- summary(mod)
  
  Rsquared_Long_H[i] <- summary$r.squared
  Fitvalue_Long <- mod$fitted.values
  
  Time_fitline <- linear_dataset$time
  
  Fitline_Long <- cbind(Time_fitline, Fitvalue_Long)
  Fitline_Long <- as.data.frame(Fitline_Long)
  
  list_Fitline_Long_H[[i]] <- Fitline_Long
  
  #df <- as.data.frame(cbind(Time_fitline, Fitvalue_Long, Squared_distance_long))
  #PRINT <- df%>%
  #  ggplot(aes(x=Time_fitline, y=Squared_distance_long)) +
  #  geom_line()+
  #  geom_line(y=Fitvalue_Long)
  #print(PRINT)
  }
summary(Rsquared_Long_H)

summary(Hurst_Fast)

```


## Calculation Of Cross Over

```{r}
for(i in 1:1204){
mycoeffmatrix <- matrix(c(-Hurst_Fast[i], 1, -Hurst_Slow[i], 1), nrow=2, ncol = 2, byrow=TRUE)
myRhsMatrix <- matrix(c(X0_Value_Fast_H[i], X0_Value_Slow_H[i]), nrow=2, ncol = 1, byrow=TRUE)
myInverse <- solve(mycoeffmatrix)
myResult <- myInverse%*%myRhsMatrix

Time_Crossover_H[i] <- myResult[1,1]
Result_Crossover_H[i] <- myResult[2,1]

list_my_Results_H[[i]] <- myResult

}

summary(Time_Crossover_H)

```


# EO X SAVE


## Data wrangling


```{r message=FALSE, warning=FALSE}
Subj <- as.numeric(names_1)
trial <- as.numeric(trial)
Subjtrial <- names

stabilogram_EO_R <- cbind.data.frame(Subj, Diff_Fast, Diff_Slow, Time_Crossover, Fit_time_value, Hurst_Fast, Hurst_Slow, Time_Crossover_H, Fit_time_value_H, Result_Crossover, trial, Subjtrial)

colnames(stabilogram_EO_R) <- c("Subj", "d_s", "d_l", "d_cx", "d_segm", "h_s", "h_l", "h_cx", "h_segm", "d_cy", "trial", "Subjtrial")

options("scipen"=100, "digits"=4)

stabilogram_EO_R <- pivot_longer(stabilogram_EO_R, cols=c("d_s", "d_l", "d_cx", "d_segm", "h_s", "h_l", "h_cx", "h_segm", "d_cy"), names_to = "Param")



stabilogram_EO_R$Subjtrial <- NULL
stabilogram_EC_R$trial <- 1
stabilogram_TR_R$trial <- 1

stabilogram_EO_R$Stance <- "EO"
stabilogram_EC_R$Stance <- "EC"
stabilogram_TR_R$Stance <- "TR"


stabilogram_parameters <-  rbind.data.frame(stabilogram_EO_R, stabilogram_EC_R, stabilogram_TR_R)

stabilogram_parameters <- stabilogram_parameters %>%
  pivot_wider(names_from = Param, values_from = value, id_cols = c(Subj, trial, Stance))

setwd("C:\\Research data\\Postural_Control_Github\\preprocessing_data")
save(stabilogram_parameters, file="stabilogram_parameters.Rdata")



```








