
# In this script we add all data files together and do the preprocessing


```{r message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(car)
library(lme4)
library(hypr) 
library(remef)
library(broom.mixed)
library(tidyverse)
library(performance)
library(parameters)
library(see)
library(summarytools)
library(lmerTest)
```


# Merging participant info, summary statistics and diffusion parameters

+ loading all files
+ merging bio (participant info) to stabilogram parameters and merging stabilogram parameters to summary statistics


```{r}
setwd("C:\\Research data\\Postural_Control_Github\\preprocessing_data")

# Load files
load(file="bio.Rdata")
load(file="stabilogram_parameters.Rdata")
load(file="summary_statistics.Rdata")
load(file="bmi_norms.Rdata")

# Reordering/selecting correct columns
participant_info <- BIO[,c(1,3,11,2,5,12,7)]

# Merging
LS3_total <- merge(participant_info, stabilogram_parameters, by = c("Subj"))
LS3_total <- merge(LS3_total, summary_statistics, by = c("Subj", "trial", "Stance"))


```

# Preprocessing

+ estimate length for 5 participants with missing length

```{r}

# PP 108, 219, 227, 410, 428 missing (3 Children, 2 Young adults) 

# Estimation (this can probably be done in an elegant way but I got stuck so I chose a practical way)
# Also, the participant with the highest mass is NA, so he gets a length of 214 cm, while he is probably overmass. 

# Participant 428 (Sex=1 group=CH)
# Select the group

df <- LS3_total %>% filter(Agegroup=="CH" & Sex == "1")

# Estimate LM
mod <- lm(df$Length ~  poly(df$mass, 2, raw = TRUE))

# Estimate length participant based on mass
l428 <- as.numeric(mod$coefficients[1]+(mod$coefficients[2]*df$mass[which(df$Subj %in% "428")][1])+(mod$coefficients[3]*df$mass[which(df$Subj %in% "428")][1]^2)) # Intercept + Mass*Coefficient

# Replace NA 
LS3_total$Length[which(LS3_total$Subj %in% "428")] <- l428


##############################################################

# Participant 410+108 (Sex=2 group=CH)
# Select the group
df <- LS3_total %>% filter(Agegroup=="CH" & Sex == "2" )

# Estimate LM
mod <- lm(df$Length ~  poly(df$mass, 2, raw = TRUE))

# Estimate length participant based on mass
l410 <- as.numeric(mod$coefficients[1]+(mod$coefficients[2]*df$mass[which(df$Subj %in% "410")][1])+(mod$coefficients[3]*df$mass[which(df$Subj %in% "410")][1]^2)) # Intercept + Mass*Coefficient

# Replace NA 
LS3_total$Length[which(LS3_total$Subj %in% "410")] <- l410

# Estimate length participant based on mass
l108 <- as.numeric(mod$coefficients[1]+(mod$coefficients[2]*df$mass[which(df$Subj %in% "108")][1])+(mod$coefficients[3]*df$mass[which(df$Subj %in% "108")][1]^2)) # Intercept + Mass*Coefficient

# Replace NA 
LS3_total$Length[which(LS3_total$Subj %in% "108")] <- l108

##############################################################

# Participant 219+227 (Sex=2 group=YA)
# Select the group
df <- LS3_total %>% filter(Agegroup=="YA" & Sex == "2" )

# Estimate LM
mod <- lm(df$Length ~  poly(df$mass, 2, raw = TRUE))

# Estimate length participant based on mass
l219 <- as.numeric(mod$coefficients[1]+(mod$coefficients[2]*df$mass[which(df$Subj %in% "219")][1])+(mod$coefficients[3]*df$mass[which(df$Subj %in% "219")][1]^2)) # Intercept + Mass*Coefficient

# Replace NA 
LS3_total$Length[which(LS3_total$Subj %in% "219")] <- l219

# Estimate length participant based on mass
l227 <- as.numeric(mod$coefficients[1]+(mod$coefficients[2]*df$mass[which(df$Subj %in% "227")][1])+(mod$coefficients[3]*df$mass[which(df$Subj %in% "227")][1]^2)) # Intercept + Mass*Coefficient

# Replace NA 
LS3_total$Length[which(LS3_total$Subj %in% "227")] <- l227


```


# Data wrangling

+ select the "best performance" trial in stable stance
+ rename factors to upper case, dependent variables/covariates to lower case
+ relevel factors
+ rename and transform measures
    + d_s = short-term diffusion coefficient
    + d_l = long-term diffusion coefficient
    + d_cx = Critical delay
+ compute linear within-group covariates age, mass, height


```{r}
df_w <-  
  LS3_total %>%  
  rename(
    age = Age,
    height = Length,
    ellipse = A_ELLIPSE,
    planar = PL_PTH) %>%  
  group_by(Subj, Stance) %>%  
  filter(ellipse == min(ellipse)) %>%  
  mutate(
    bmi = mass / ((height/100)^2),
    Group = as_factor(ifelse(age<15, "CH", ifelse(age>15 & age<40, "YA" , "OA"))),
    Group = fct_relevel(Group, "CH", "YA", "OA"),
    Sex = recode(as_factor(Sex),"1" = "Female" , "2" = "Male"),
    Stance = recode(as_factor(Stance),"EO" = "SS" ),
    Stance = as_factor(Stance),
    Stance = fct_relevel(Stance, "EC", "SS", "TR"),
    d_s = d_s*1000,       # from mm²/ms to mm²/s
    d_l = d_l*1000,       # from mm²/ms to mm²/s
    d_cx = d_cx/1000,
    d_segm = d_segm/1000,) %>%   # from ms to s
  group_by(Group) %>%  
  mutate(a1 = age - mean(age), 
         m1 = mass - mean(mass), 
         h1 = height - mean(height, na.rm=TRUE)) %>%  
  select(Subj, Group, Sex, age,  mass, height, bmi, a1, m1, h1, Stance, d_s, d_l, d_cx, d_segm)

df <- 
  df_w %>%  
  pivot_longer(d_s:d_segm, names_to="Measure", values_to="score")

```

# Calculate "bmi_score" based on age and sex specific norms. 

```{r}
# Round age (only have norms until 79 yo )
df <- df %>% mutate(age_round = ifelse(age<18, (round(age/0.5)*0.5),  round(age)) )
df <- df %>% mutate(age_round = ifelse(age_round>79, 79,  age_round ))

# Calculation of bmi score    ==   SDS (x;a) = (BMI / M(a))^L(a)-1/(L(a)*S(a)) 

### Selecting the correct row in norm table 

bmi_row <- vector()
for(i in 1:nrow(df)) {bmi_row[i]  <- which(df$age_round[i] == bmi_norms$age & df$Sex[i]  == bmi_norms$Sex)}
df$bmi_row <- bmi_row

### Calculation
df <- df %>% 
  mutate(bmi_score = (((bmi/bmi_norms$M[bmi_row])^bmi_norms$L[bmi_row])-1 ) /(bmi_norms$L[bmi_row]*bmi_norms$S[bmi_row]))

### Mean center BMI
df <-  
  df %>%  
  group_by(Group) %>%  
  mutate(bmi1 = bmi_score - mean(bmi_score)) 

```


# Corrections

+ Outliers identified below should be corrected or removed in this chunk.

```{r}
# The CoP trajectory of this trial shows that the participant lifted up one leg/fell.
df <- df %>%   mutate(score = ifelse( Subj== "165" & Stance == "TR", NA, score))
df <- df %>%  mutate(score = ifelse( Subj== "176" & Stance == "TR", NA, score))

# methodological flaw (crossover point is the intercept of the two regression lines)
df <- df %>%  mutate(score = ifelse( Subj== "6271" & Stance == "TR" & Measure =="d_cx", NA, score))

# Participant with club (n=1) feet and ADHD (n=1)
df <- df %>%   mutate(score = ifelse(Subj== c("1071", "1081" ), NA, score)) 

# Technical error? Always same pattern in sway across all movement, seems artificial

df <- df %>%  mutate(score = ifelse( Subj== "724" & Stance == "TR", NA, score))


# Fit procedure failed, extremely bad fit, segmented did not select "correct point". 

df <- df %>%  mutate(score = ifelse( Subj== "613" & Stance == "EC", NA, score))
df <- df %>%  mutate(score = ifelse( Subj== "120" & Stance == "TR", NA, score))
df <- df %>%  mutate(score = ifelse( Subj== "6271" & Stance == "TR", NA, score))


# delete missing scores
df <- df %>%  filter(!is.na(score))


```



# Linear Mixed Models

## Defining Contrasts

```{r}

contrasts(df$Sex) <- MASS::contr.sdif(2)

my.contrast = matrix(c(0.6666667, -0.3333333, -0.3333333, -0.3333333, -0.3333333, 0.6666667), ncol = 2)
colnames(my.contrast) <- c("EC-SS", "TR-SS")
rownames(my.contrast) <- rownames(MASS::contr.sdif(3))

contrasts(df$Stance) <- my.contrast

colnames(my.contrast) <- c("CH-YA", "OA-YA")
contrasts(df$Group) <- my.contrast

```


# LMM1 - d_s

## Select a transformation

```{r}
# Select variable
df_s <-   df %>%  filter(Measure == "d_s")

# Select model matrix
modmat_s <- model.matrix( ~  1 + Stance*(Group/(Sex*a1*bmi1)) , df_s )
df_s$st1 <- modmat_s[,2]
df_s$st2 <- modmat_s[,3]

# transform data
df_s$tscore <- log10(df_s$score) # Transformation needed

# Run base model
t_mm_s1 <- lmer(tscore ~ 1 +  Stance*(Group/(Sex*a1*bmi1)) + (1| Subj), 
                    data = df_s, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
check_model(t_mm_s1)
print(summary(t_mm_s1), corr=FALSE)

```

## Reduce Fixed Effects

### 1. Remove Sex
```{r} 
t_mm_s2 <- lmer(tscore ~ 1 + Stance*(Group/(a1*bmi1)) + (1| Subj), 
                    data = df_s, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
print(summary(t_mm_s2), corr=FALSE)
```

### 2. Remove a1:bmi1 and a1: ... : ...                                                
```{r}
# Remove covariate * covariate interactions and other irelevant covariate interactions
modmat_s <- model.matrix( ~  1 + Stance*(Group/(a1*bmi1)) , df_s )
t_mm_s3 <- lmer(tscore ~ 1 + modmat_s[, c(2:15, 25:30) ] + (1| Subj), 
                 data = df_s, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
print(summary(t_mm_s3), corr=FALSE)

```

### 3. Remove BMI? 
```{r}
modmat_s <- model.matrix( ~  1 + Stance*(Group/(a1)) , df_s )

t_mm_s4 <- lmer(tscore ~ 1 + modmat_s[, c(2:12) ] + (1| Subj), 
                 data = df_s, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
print(summary(t_mm_s4), corr=FALSE)

```

## Compare models
```{r}
anova( t_mm_s2, t_mm_s1)
anova( t_mm_s2, t_mm_s3)
anova( t_mm_s4, t_mm_s3)
```

### 4. Expand RE - Including BMI 
```{r}
modmat_s <- model.matrix( ~  1 + Stance*(Group/(a1*bmi1)) , df_s )
t_mm_s4 <- lmer(tscore ~ 1 + modmat_s[, c(2:15, 25:30) ]  + (1 + st1 + st2 ||  Subj), 
                 data = df_s, REML = FALSE, #
                 control=lmerControl(calc.derivs=FALSE, check.nobs.vs.nRE="ignore"))
```

### 5. Expand RE - Removed BMI 
```{r}
modmat_s <- model.matrix( ~  1 + Stance*(Group/(a1)) , df_s )
t_mm_s5 <- lmer(tscore ~ 1 + modmat_s[, c(2:12) ] + (1 + st1 + st2 ||  Subj), 
                 data = df_s, REML = FALSE, #
                 control=lmerControl(calc.derivs=FALSE, check.nobs.vs.nRE="ignore"))

print(summary(t_mm_s4), corr=FALSE)
print(summary(t_mm_s5), corr=FALSE)

```

## Excursion to levels

```{r}
# Excursion to estimate VCs and CPs for scores/levels of Stance, not effects
modmat_s0 <- model.matrix( ~  0 + Stance*(Group/(Sex*a1)), df_s )
df_s$TR <- modmat_s0[,1]
df_s$SS <- modmat_s0[,2]
df_s$EC <- modmat_s0[,3]

t_mm_sLvls <- lmer(tscore ~ 1 + modmat_s[,2:15] + (0 + TR + SS + EC  |  Subj), 
                 data = df_s, REML = FALSE, 
                 control=lmerControl(calc.derivs=FALSE, check.nobs.vs.nRE="ignore"))

VarCorr(t_mm_sLvls)
```







## Graphs

### Recode variables

```{r}
df_s$Group <- recode(df_s$Group, CH = "Children", YA = "Young Adults", OA = "Older Adults" )
df_s$Stance <- recode(df_s$Stance, SS = "Stable Stance", EC = "Eyes Closed", TR = "Tandem Romberg" )
df_s$Stance <- factor(df_s$Stance, levels = c("Stable Stance", "Eyes Closed", "Tandem Romberg"))
```

### Group x Stance

```{r}
df_s %>%  
  group_by(Group, Stance) %>%  
  summarize(N=n(), tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=Group, y=10^tscore_M, group=Stance, color=Stance)) +
  geom_point( position=position_dodge(.2)) + geom_line( position=position_dodge(.2)) +
  geom_errorbar(aes(ymax=10^(tscore_M+2*SE), ymin=10^(tscore_M-2*SE)), width=.2,  position=position_dodge(.2)) +
  theme_bw() +   ylab(bquote(Short-Term~Diffusion~Coefficient~(mm^2~s^-1)))   +  xlab("") + scale_y_log10() 

```

### BMI x Stance

```{r}
df_s %>%  
  group_by(Group, Stance, Subj) %>%  
  summarize(N=n(), bmi1 = first(bmi1),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=bmi1, y=10^tscore_M, group=Stance, color=Stance)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  ylab(bquote(Short-Term~Diffusion~Coefficient~(mm^2~s^-1))) +
  theme_bw() + scale_y_log10() 

```

### a1 x Group --> all Stances collapsed

```{r}
df_s %>%  
  group_by(Group, Subj) %>%  
  summarize(N=n(), age_c = first(a1),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=age_c, y=10^tscore_M, group=1)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  facet_grid(. ~ Group) +
  ylab(bquote(Short-Term~Diffusion~Coefficient~(mm^2~s^-1))) +
  xlab("Mean-Centered Age Coefficient (years)") +
  theme_bw() + scale_y_log10() 

```


### a1 x Group 

```{r}
df_s %>%  
  group_by(Group, Stance, Subj) %>%  
  summarize(N=n(), age_c = first(a1),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=age_c, y=10^tscore_M, group=Stance)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE, aes( color = Stance)) +
  ylab(bquote(Short-Term~Diffusion~Coefficient~(mm^2~s^-1))) +
  facet_grid(. ~ Group) +
  theme_bw() + scale_y_log10() +
    xlab("Mean-Centered Age Coefficient (years)") 
```

# Plot BMI * Stance * Group

```{r}
df_s %>%  
  group_by(Stance, Group, Subj) %>%  
  summarize(N=n(), Sex = first(Sex), bmi_score = first(bmi_score),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=bmi_score, y=10^tscore_M, group=Stance, color=Stance)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  theme_bw() +
  facet_wrap(.~Group) + scale_y_log10() +   ylab(bquote(Short-Term~Diffusion~Coefficient~(mm^2~s^-1))) + xlab("Z-score Body Mass Index [± SD]")

```







# LMM2 - d_l

## Select a transformation

```{r  }
df_l <-   df %>%  filter(Measure == "d_l") # Select variable

# setup model matrix and stance model coefficients
modmat_l <- model.matrix( ~  1 + Stance*(Group/(Sex*a1)), df_l )
df_l$st1 <- modmat_l[,2]
df_l$st2 <- modmat_l[,3]

mm_l1 <- lmer(score ~ 1 + Stance*(Group/(Sex*a1*bmi1))+ (1| Subj), 
                    data = df_l, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
#check_model(mm_l1)

# power transform for LMM residuals: 
pt_l <- powerTransform(mm_l1, family="bcnPower")
summary(pt_l)


## - lambda= -0.0884    , not different from zero
## -  gamma= 0.8412    ;  different from zero  

# transformed score

df_l$tscore <- bcnPower(df_l$score, lambda=0, gamma=.85) 

# refit LMM
t_mm_l1 <- lmer(tscore ~ 1 + Stance*(Group/(Sex*a1*bmi1))+ (1| Subj), 
                    data = df_l, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
check_model(t_mm_l1)
print(summary(t_mm_l1), corr=FALSE)


```

## Reduce FEs

### 1. Remove Sex

```{r}
t_mm_l2 <- lmer(tscore ~ 1 + Stance*(Group/(a1*bmi1))+ (1| Subj), 
                    data = df_l, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
print(summary(t_mm_l2), corr=FALSE)
```

### 2. Remove interactions a1:bmi1:... 
```{r}
modmat_l <- model.matrix( ~  1 +Stance*(Group/(a1*bmi1)), df_l )
t_mm_l3 <- lmer(tscore~ 1 + modmat_l[,c(2:15, 19:30) ] + (1| Subj),
                   data = df_l, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
print(summary(t_mm_l3), corr=FALSE)
```

### 2. Remove  bmi1

```{r}

modmat_l <- model.matrix( ~  1 +Stance*(Group/(a1)), df_l )
df_l$st1 <- modmat_l[,2]
df_l$st2 <- modmat_l[,3]

t_mm_l4 <- lmer(tscore~ 1 + modmat_l[,2:18] + (1| Subj),
                   data = df_l, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
print(summary(t_mm_l4), corr=FALSE)



```

# Compare models
```{r}
anova( t_mm_l2, t_mm_l1) # nearly all noise
anova( t_mm_l2, t_mm_l3) # All noise
anova( t_mm_l4, t_mm_l3) # significantly different

```

## Expand RE

### including BMI
```{r}
modmat_l <- model.matrix( ~  1 +Stance*(Group/(a1)), df_l)
t_mm_l5 <- lmer(tscore~ 1 + modmat_l[,2:18] + (1+ st1 + st2 || Subj),
                   data = df_l, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
print(summary(t_mm_l5), corr=FALSE)
```

### excluding BMI
```{r}
modmat_l <- model.matrix( ~  1 + Stance *(Group/(a1*bmi1)), df_l )
t_mm_l6 <- lmer(tscore~ 1 + modmat_l[,c(2:15, 19:30) ] + (1+ st1 + st2 || Subj),
                   data = df_l, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
print(summary(t_mm_l6), corr=FALSE)
```

# Compare models
```{r}
anova( t_mm_l6, t_mm_l5) # significantly different

```







## Graphs

### Recode variables

```{r}
df_l$Group <- recode(df_l$Group, CH = "Children", YA = "Young Adults", OA = "Older Adults" )
df_l$Stance <- recode(df_l$Stance, SS = "Stable Stance", EC = "Eyes Closed", TR = "Tandem Romberg" )
df_l$Stance <- factor(df_l$Stance, levels = c("Stable Stance", "Eyes Closed", "Tandem Romberg"))
```


### Group x Stance

```{r}
df_l %>%  
  group_by(Group, Stance) %>%  
  summarize(N=n(), tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=Group, y=bcnPowerInverse(tscore_M, lambda=0, gamma=.85), group=Stance, color=Stance)) +
  geom_point( position=position_dodge(.2)) + geom_line( position=position_dodge(.2)) +
  geom_errorbar(aes(ymax=bcnPowerInverse(tscore_M+2*SE, lambda=0, gamma=.85), ymin=bcnPowerInverse(tscore_M-2*SE, lambda=0, gamma=.85)), width=.2,  position=position_dodge(.2)) +
  theme_bw() +   ylab(bquote(Long-Term~Diffusion~Coefficient~(mm^2~s^-1)))   +  xlab("") + scale_y_log10()

```

### BMI x Stance

```{r}
library(ggallin)

df_l %>%  
  group_by(Group, Stance, Subj) %>%  
  summarize(N=n(), bmi1 = first(bmi1),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=bmi1, y=bcnPowerInverse(tscore_M, lambda=0, gamma=.85), group=Stance, color=Stance)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  ylab(bquote(Long-Term~Diffusion~Coefficient~(mm^2~s^-1)))  +
  theme_bw() + scale_y_continuous(trans = pseudolog10_trans)

```

### a1 x Group --> all Stances collapsed

```{r}
df_l %>%  
  group_by(Group, Subj) %>%  
  summarize(N=n(), age_c = first(a1),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=age_c, y=bcnPowerInverse(tscore_M, lambda=0, gamma=.85), group=1)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  facet_grid(. ~ Group) +
  ylab(bquote(Long-Term~Diffusion~Coefficient~(mm^2~s^-1))) +
  xlab("Mean-Centered Age Coefficient (years)") +
  theme_bw() + scale_y_continuous(trans = pseudolog10_trans)

```


### a1 x Group 

```{r}
df_l %>%  
  group_by(Group, Stance, Subj) %>%  
  summarize(N=n(), age_c = first(a1),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=age_c, y=bcnPowerInverse(tscore_M, lambda=0, gamma=.85), group=Stance)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE, aes( color = Stance)) +
  ylab(bquote(Long-Term~Diffusion~Coefficient~(mm^2~s^-1)))  +
  facet_grid(. ~ Group) +
  theme_bw() +  scale_y_continuous(trans = pseudolog10_trans)+
    xlab("Mean-Centered Age Coefficient (years)") 
```

# Plot BMI * Stance * Group

```{r}
df_l %>%  
  group_by(Stance, Group, Subj) %>%  
  summarize(N=n(), Sex = first(Sex), bmi_score = first(bmi_score),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=bmi_score, y=bcnPowerInverse(tscore_M, lambda=0, gamma=.85), group=Stance, color=Stance)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  theme_bw() +
  facet_wrap(.~Group)  + scale_y_continuous(trans = pseudolog10_trans) +   ylab(bquote(Long-Term~Diffusion~Coefficient~(mm^2~s^-1)))  + xlab("Z-score Body Mass Index [± SD]")

```









# LMM3 - d_segm 

## Select a transformation

```{r  }
# Selecting the variable
df_segm <-  df %>%  filter(Measure == "d_segm")

# Select model matrix
modmat_segm <- model.matrix( ~  1 + Stance*(Group/(Sex*a1*bmi1)) , df_segm )
df_segm$st1 <- modmat_s[,2]
df_segm$st2 <- modmat_s[,3]

# it might be better for plotting/transparency/reproducibility to use log transform
df_segm$tscore <- log10(df_segm$score)

# LMM
t_mm_segm1 <- lmer(tscore ~ 1 + Stance*(Group/(Sex*a1*bmi1)) + (1| Subj), 
                data = df_segm, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
check_model(t_mm_segm1)
print(summary(t_mm_segm1), corr=FALSE)

```

## Reduce Fixed Effects

### 1. Remove Sex
```{r} 
t_mm_segm2 <- lmer(tscore ~ 1 + Stance*(Group/(a1*bmi1)) + (1| Subj), 
                    data = df_segm, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
print(summary(t_mm_segm2), corr=FALSE)
```

### 2. Remove a1:bmi1 and a1: ... : ...                                                
```{r}
# Remove covariate * covariate interactions and other irelevant covariate interactions
modmat_segm <- model.matrix( ~  1 + Stance*(Group/(a1*bmi1)) , df_segm )
t_mm_segm3 <- lmer(tscore ~ 1 + modmat_segm[, c(2:15, 25:30) ] + (1| Subj), 
                 data = df_segm, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
print(summary(t_mm_segm3), corr=FALSE)

```

### 3. Remove BMI? 
```{r}
modmat_segm <- model.matrix( ~  1 + Stance*(Group/(a1)) , df_s )

t_mm_segm4 <- lmer(tscore ~ 1 + modmat_segm[, c(2:12) ] + (1| Subj), 
                 data = df_segm, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
print(summary(t_mm_segm4), corr=FALSE)

```

## Compare models
```{r}
anova( t_mm_segm2, t_mm_segm1) # Remove Sex 61.64 36    0.00493 **
anova( t_mm_segm2, t_mm_segm3) # Remove noise
anova( t_mm_segm4, t_mm_segm3) # Remove BMI
```

### 4. Expand RE - Including BMI 
```{r}
modmat_segm <- model.matrix( ~  1 + Stance*(Group/(a1*bmi1)) , df_segm )
t_mm_segm5 <- lmer(tscore ~ 1 + modmat_segm[, c(2:15, 25:30) ]  + (1 + st1 + st2 ||  Subj), 
                 data = df_segm, REML = FALSE, #
                 control=lmerControl(calc.derivs=FALSE, check.nobs.vs.nRE="ignore"))
```

### 5. Expand RE - Removed BMI 
```{r}
modmat_segm <- model.matrix( ~  1 + Stance*(Group/(a1)) , df_segm )
t_mm_segm6 <- lmer(tscore ~ 1 + modmat_segm[, c(2:12) ] + (1 + st1 + st2 ||  Subj), 
                 data = df_segm, REML = FALSE, #
                 control=lmerControl(calc.derivs=FALSE, check.nobs.vs.nRE="ignore"))

print(summary(t_mm_segm5), corr=FALSE)
print(summary(t_mm_segm6), corr=FALSE)

```


```{r}
anova(t_mm_segm5, t_mm_segm3)
anova(t_mm_segm6, t_mm_segm4) # Model 6
```



## Graphs

### Recode variables

```{r}
df_segm$Group <- recode(df_segm$Group, CH = "Children", YA = "Young Adults", OA = "Older Adults" )
df_segm$Stance <- recode(df_segm$Stance, SS = "Stable Stance", EC = "Eyes Closed", TR = "Tandem Romberg" )
df_segm$Stance <- factor(df_segm$Stance, levels = c("Stable Stance", "Eyes Closed", "Tandem Romberg"))
```

### Group x Stance

```{r}
df_segm %>%  
  group_by(Group, Stance) %>%  
  summarize(N=n(), tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=Group, y=10^tscore_M, group=Stance, color=Stance)) +
  geom_point( position=position_dodge(.2)) + geom_line( position=position_dodge(.2)) +
  geom_errorbar(aes(ymax=10^(tscore_M+2*SE), ymin=10^(tscore_M-2*SE)), width=.2,  position=position_dodge(.2)) +
  theme_bw() +   ylab("Critical Delay (s)")  +  xlab("") + scale_y_log10() 

```

### BMI x Stance

```{r}
df_segm %>%  
  group_by(Group, Stance, Subj) %>%  
  summarize(N=n(), bmi1 = first(bmi1),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=bmi1, y=10^tscore_M, group=Stance, color=Stance)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  ylab("Critical Delay (s)")  +
  theme_bw() + scale_y_log10() 

```

### a1 x Group --> all Stances collapsed

```{r}
df_segm %>%  
  group_by(Group, Subj) %>%  
  summarize(N=n(), age_c = first(a1),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=age_c, y=10^tscore_M, group=1)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  facet_grid(. ~ Group) +
  ylab("Critical Delay (s)")  +
  xlab("Mean-Centered Age Coefficient (years)") +
  theme_bw() + scale_y_log10() 

```


### a1 x Group 

```{r}
df_segm %>%  
  group_by(Group, Stance, Subj) %>%  
  summarize(N=n(), age_c = first(a1),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=age_c, y=10^tscore_M, group=Stance)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE, aes( color = Stance)) +
  ylab("Critical Delay (s)")  +
  facet_grid(. ~ Group) +
  theme_bw() + scale_y_log10() +
    xlab("Mean-Centered Age Coefficient (years)") 
```

# Plot BMI * Stance * Group

```{r}
df_segm %>%  
  group_by(Stance, Group, Subj) %>%  
  summarize(N=n(), Sex = first(Sex), bmi_score = first(bmi_score),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=bmi_score, y=10^tscore_M, group=Stance, color=Stance)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  theme_bw() +
  facet_wrap(.~Group) + scale_y_log10() +   ylab("Critical Delay (s)") + xlab("Z-score Body Mass Index [± SD]")

```


# Appendix

```{r}
sessionInfo()
```



