# In this script we add all data files together and do the preprocessing


```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(car)
library(lme4)
library(hypr) 
library(remef)
library(broom.mixed)
library(tidyverse)
library(performance)
library(parameters)
library(see)
library(summarytools)
```


# Merging participant info, summary statistics and diffusion parameters

+ loading all files
+ merging bio (participant info) to stabilogram parameters and merging stabilogram parameters to summary statistics


```{r}

# Load files

setwd("C:\\Research data\\Postural_Control_Github\\preprocessing_data")
file <- Sys.glob("*")
for(i in 1:3){
  load(file= file[i])
}

# Reordering/selecting correct columns
BIO <- BIO[,c(1,3,11,2,5,6,7)]

# Merging
merge <- merge(BIO, stabilogram_parameters, by = c("Subj"))
LS3_total <- merge(merge, summary_statistics, by = c("Subj", "trial", "Stance"))


```

# Preprocessing

+ select the "best performance" trial in stable stance
+ rename factors to upper case, dependent variables/covariates to lower case
+ relevel factors
+ rename and transform measures
    + d_s = short-term diffusion coefficient
    + d_l = long-term diffusion coefficient
    + d_cx = Critical delay
+ compute linear within-group covariates age, mass, height


```{r}

df_w <-  
  LS3_total %>%  
  rename(
    age = Age,
    height = Length,
    mass = Weight,
    bmi = BMI,
    ellipse = A_ELLIPSE,
    planar = PL_PTH) %>%  
  group_by(Subj, Stance) %>%  
  filter(ellipse == min(ellipse)) %>%  
  mutate(
    Group = as_factor(ifelse(age<15, "CH", ifelse(age>15 & age<40, "YA" , "OA"))),
    Group = fct_relevel(Group, "CH", "YA", "OA"),
    Sex = recode(as_factor(Sex),"1" = "Female" , "2" = "Male"),
    Stance = recode(as_factor(Stance),"EO" = "SS" ),
    Stance = as_factor(Stance),
    Stance = fct_relevel(Stance, "TR", "SS", "EC"),
    d_s = d_s*1000,       # from mm²/ms to mm²/s
    d_l = d_l*1000,       # from mm²/ms to mm²/s
    d_cx = d_cx/1000,
    d_segm = d_segm/1000,) %>%   # from ms to s
  group_by(Group) %>%  
  mutate(a1 = age - mean(age), 
         m1 = mass - mean(mass), 
         h1 = height - mean(height, na.rm=TRUE)) %>%  
  select(Subj, Group, Sex, age,  mass, height, bmi, a1, m1, h1, Stance, d_s, d_l, d_cx, d_segm)

df <- 
  df_w %>%  
  pivot_longer(d_s:d_segm, names_to="Measure", values_to="score")


```

# Corrections

Outliers identified below should be corrected or removed in this chunk.

```{r}
# The CoP trajectory of this trial shows that the participant lifted up one leg/fell.
df <- df %>%   mutate(score = ifelse( Subj== "165" & Stance == "TR", NA, score))

# methodological flaw (crossover point is the intercept of the two regression lines)
df <- df %>%  mutate(score = ifelse( Subj== "6271" & Stance == "TR" & Measure =="d_cx", NA, score))

# delete missing scores
df <- df %>%  filter(!is.na(score))
```

# LMM1 - d_s

## Select a transformation

```{r include=FALSE}
df_s <-   df %>%  filter(Measure == "d_s")

contrasts(df_s$Stance) <- MASS::contr.sdif(3)
contrasts(df_s$Group) <- MASS::contr.sdif(3)
contrasts(df_s$Sex) <- MASS::contr.sdif(2)

mm_s1 <- lmer(score ~ 1 + Stance*(Group/(Sex*a1)) + (1| Subj), 
                    data = df_s, REML = FALSE, 
              control = lmerControl(calc.derivs=FALSE, check.nobs.vs.nRE="ignore" ))
check_model(mm_s1)

# power transform for LMM residuals
pt_s <- powerTransform(mm_s1, family="bcnPower")
summary(pt_s)
## - lambda=-0.03149194, not diff from zero
## -  gamma=0.1; not far from zero either, anyway ...

# transformed score
df_s$tscore <- bcnPower(df_s$score, lambda=0, gamma=0.1)

# refit LMM
t_mm_s1 <- lmer(tscore ~ 1 + Stance*(Group/(Sex*a1)) + (1| Subj), 
                    data = df_s, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
check_model(t_mm_s1)

print(summary(t_mm_s1), corr=FALSE)
```

## Reduce FEs

```{r include=FALSE}
t_mm_s2 <- lmer(tscore ~ 1 + (Stance+Group/(Sex+a1))^2+ (1| Subj), 
                    data = df_s, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
anova(t_mm_s2, t_mm_s1)

print(summary(t_mm_s2), corr=FALSE)

modmat_s <- model.matrix( ~  1 + Stance*(Group/(Sex*a1)), df_s )

t_mm_s3 <- lmer(tscore ~ 1 + modmat_s[, 2:15 ] + (1| Subj), 
                 data = df_s, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))

anova(t_mm_s3, t_mm_s2, t_mm_s1)
anova(t_mm_s3, t_mm_s1)

print(summary(t_mm_s3), corr=FALSE)
```

## Expand REs

```{r include=FALSE}
df_s$st1 <- modmat_s[,2]
df_s$st2 <- modmat_s[,3]

t_mm_s4 <- lmer(tscore ~ 1 + modmat_s[,2:15] + (1 + st1 + st2 ||  Subj), 
                 data = df_s, REML = FALSE, #
                 control=lmerControl(calc.derivs=FALSE, check.nobs.vs.nRE="ignore"))

anova(t_mm_s3, t_mm_s4)
print(summary(t_mm_s4), corr=FALSE)

t_mm_s5 <- lmer(tscore ~ 1 + modmat_s[,2:15] + (1 + st1 + st2 | Subj), 
                 data = df_s, REML = FALSE, #
                 control=lmerControl(calc.derivs=FALSE, check.nobs.vs.nRE="ignore"))
print(summary(t_mm_s5), corr=FALSE)
anova(t_mm_s3, t_mm_s4, t_mm_s5)  # Stay with 4
```

## Excursion to levels

```{r}
# Excursion to estimate VCs and CPs for scores/levels of Stance, not effects
modmat_s0 <- model.matrix( ~  0 + Stance*(Group/(Sex*a1)), df_s )
df_s$TR <- modmat_s0[,1]
df_s$SS <- modmat_s0[,2]
df_s$EC <- modmat_s0[,3]

t_mm_sLvls <- lmer(tscore ~ 1 + modmat_s[,2:15] + (0 + TR + SS + EC  |  Subj), 
                 data = df_s, REML = FALSE, #
                 control=lmerControl(calc.derivs=FALSE, check.nobs.vs.nRE="ignore"))
```

## Graphs

### Group x Stance

```{r}
df_s %>%  
  group_by(Group, Stance) %>%  
  summarize(N=n(), tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=Group, y=tscore_M, group=Stance, color=Stance)) +
  geom_point() + geom_line() +
  geom_errorbar(aes(ymax=tscore_M+2*SE, ymin=tscore_M-2*SE), width=.01) +
#  geom_smooth() +
  theme_bw()
```

### age  x  Group

```{r}
df_s %>%  
  group_by(Group, Subj) %>%  
  summarize(N=n(), age_c = first(a1),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=age_c, y=tscore_M, group=1, color=1)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  facet_grid(. ~ Group) +
  theme_bw()
```

### Sex  x  Group

```{r}
df_s %>%  
  group_by(Group, Sex, Subj) %>%  
  summarize(N=n(),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=Group, y=tscore_M)) + 
  geom_boxplot(aes(color=Sex)) +
  theme_bw()
```

# LMM2 - d_l

## Select a transformation

```{r include=FALSE}
df_l <-   df %>%  filter(Measure == "d_l")

# remove one outlier -- looks like decimal coding error
df_l %>%  
  group_by(Group, Sex, Stance) %>%  
  summarise(N=n(), score_M=mean(score), score_SD=sd(score))
df_l[297, ]

df_l <- df_l[-297, ] 

contrasts(df_l$Stance) <- MASS::contr.sdif(3)
contrasts(df_l$Group) <- MASS::contr.sdif(3)
contrasts(df_l$Sex) <- MASS::contr.sdif(2)

modmat_l <- model.matrix( ~  1 + Stance*(Group/(Sex+a1)), df_l )
df_l$st1 <- modmat_l[,2]
df_l$st2 <- modmat_l[,3]

mm_l1 <- lmer(score ~ 1 + Stance*(Group/(Sex*a1))+ (1| Subj), 
                    data = df_l, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
check_model(mm_l1)

# power transform for LMM residuals: 
pt_l <- powerTransform(mm_l, family="bcnPower")
summary(pt_l)
## - lambda= 0.01557182, not diff from zero
## -  gamma= 0.6922534;  different from zero either 

# transformed score
df_l$tscore <- bcnPower(df_l$score, lambda=0, gamma=0.69)  

# refit LMM
t_mm_l1 <- lmer(tscore ~ 1  + Stance*(Group/(Sex*a1))+ (1| Subj), 
                    data = df_l, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
check_model(t_mm_l1)

print(summary(t_mm_l1), corr=FALSE)
```

## Reduce FEs

```{r include=FALSE}
t_mm_l2 <- lmer(tscore ~ 1 + Stance*(Group/a1) + (1| Subj), 
                    data = df_l, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
anova(t_mm_l2, t_mm_l1)

print(summary(t_mm_l2), corr=FALSE)
```

## Expand REs

```{r include=FALSE}
t_mm_l3 <- lmer(tscore ~ 1 + Stance*(Group/a1) + (1 + st1 + st2 ||  Subj), 
                 data = df_l, REML = FALSE, #
                 control=lmerControl(calc.derivs=FALSE, check.nobs.vs.nRE="ignore"))

anova(t_mm_l2, t_mm_l3)
print(summary(t_mm_l3), corr=FALSE)

t_mm_l4 <- lmer(tscore ~ 1 + Stance*(Group/a1) + (1 + st1 + st2 | Subj), 
                 data = df_l, REML = FALSE, #
                 control=lmerControl(calc.derivs=FALSE, check.nobs.vs.nRE="ignore"))
anova(t_mm_l2, t_mm_l3, t_mm_l4)  # Stay with t_mm_l4
print(summary(t_mm_l4), corr=FALSE)
```

## Graph:  age x Stance x Group 

```{r}
df_l %>%  
  group_by(Group, Stance, Subj) %>%  
  summarize(N=n(), age_c = first(a1),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=age_c, y=tscore_M, group=Stance, color=Stance)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  facet_grid(. ~ Group) +
  theme_bw()
```


# LMM3 - d_cx 

The section is still a CONSTUCTION SITE.

## Select a transformation

### Iteration 1

```{r include=FALSE}
df_cx <-  df %>%  filter(Measure == "d_cx")

contrasts(df_cx$Stance) <- MASS::contr.sdif(3)
contrasts(df_cx$Group) <- MASS::contr.sdif(3)
contrasts(df_cx$Sex) <- MASS::contr.sdif(2)

df_cx %>%  
  group_by(Group, Sex, Stance) %>%  
  summarise(N=n(), score_M=mean(score), score_SD=sd(score))

mm_cx0 <- lmer(score ~ 1  + Stance*(Group/(Sex*a1)) + (1| Subj), 
                     data = df_cx, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
check_model(mm_cx0)

# power transform for LMM residuals: 
p_cx0 <- powerTransform(mm_cx0, family="bcnPower")
## - lambda=0.208279,  different from zero
## -  gamma=0.3065152;  different from zero  

# transformed score
df_cx$tscore <- bcnPower(df_cx$score, lambda=.21, gamma=0.31)  

# refit LMM
t_mm_cx0 <- lmer(tscore ~ 1  + Stance*(Group/(Sex*a1)) + (1| Subj), 
                data = df_cx, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
check_model(t_mm_cx0)
```

### Iteration 2: 

START OVER: refit LMM to score for `df` w/o outliers.

We remove outliers identified in `t_mm_cx0`.

```{r include=FALSE}
ibad <- which(resid(t_mm_cx0) < -1)
df_cx <- df_cx[-ibad,]

contrasts(df_cx$Stance) <- MASS::contr.sdif(3)
contrasts(df_cx$Group) <- MASS::contr.sdif(3)
contrasts(df_cx$Sex) <- MASS::contr.sdif(2)

mm_cx1 <- lmer(score ~ 1  + Stance*(Group/(Sex*a1)) + (1| Subj), 
                     data = df_cx, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
check_model(mm_cx1)

# power transform for LMM residuals: 
p_cx1 <- powerTransform(mm_cx, family="bcnPower")
summary(p_cx1)
## - lambda= -0.4507433,  not different from zero
## -  gamma= 0.3769453;  different from zero  

# transformed score; we use lambda = -1/2  
df_cx$tscore <- bcnPower(df_cx$score, lambda=-.50, gamma=0.38)  

# refit LMM
t_mm_cx1 <- lmer(tscore ~ 1  + Stance*(Group/(Sex*a1)) + (1| Subj), 
                    data = df_cx, REML = FALSE, control = lmerControl(calc.derivs=FALSE ))
check_model(t_mm_cx1)

print(summary(t_mm_cx1), corr=FALSE)
```

## Reduce FEs

```{r}
modmat_cx <- model.matrix( ~  1 + Stance*(Group/(Sex*a1)), df_cx )
df_cx$st1 <- modmat_cx[,2]
df_cx$st2 <- modmat_cx[,3]

t_mm_cx2 <- lmer(tscore ~ 1 + modmat_cx[,2:15] + (1 |  Subj), 
                 data = df_cx, REML = FALSE, #
                 control=lmerControl(calc.derivs=FALSE, check.nobs.vs.nRE="ignore"))

anova(t_mm_cx2, t_mm_cx1)
print(summary(t_mm_cx2), corr=FALSE)
```

+ `Sex` could also be removed, but perhaps it is ok to keep some comparability in model complexity.

## Expand REs

```{r}
t_mm_cx3 <- lmer(tscore ~ 1 + modmat_cx[,2:15] + (1 + st1 + st2 ||  Subj), 
                 data = df_cx, REML = FALSE, #
                 control=lmerControl(calc.derivs=FALSE, check.nobs.vs.nRE="ignore"))
anova(t_mm_cx2, t_mm_cx3)

t_mm_cx4 <- lmer(tscore ~ 1 + modmat_cx[,2:15] + (1 + st1 + st2 |  Subj), 
                 data = df_cx, REML = FALSE, #
                 control=lmerControl(calc.derivs=FALSE, check.nobs.vs.nRE="ignore"))
anova(t_mm_cx2, t_mm_cx3, t_mm_cx4)
```

No improvement with VCs and CPs. We stay with `t_mm_cx1`.

## Graphs: Group x Stance

```{r}
df_cx %>%  
  group_by(Group, Stance, Subj) %>%  
  summarize(N=n(),  tscore_M = mean(tscore), SE = sd(tscore)/sqrt(N)) %>%  
  ggplot(aes(x=Group, y=tscore_M)) + 
  geom_boxplot(aes(color=Stance)) +
  theme_bw()
```

# Appendix

```{r}
sessionInfo()
```



