# Lagged Distance Calculations LS3 Study
## 10/01/2021

# We differentiate 3 difficulty manipulations: eyes open / eyes closed / tandem stance (EO/EC/TR)
# We calculate the lagged distances for anterio-posterior, medio-lateral and planar directions (X Y R) 


# 1. Eyes open 
## 1.1 Selecting X and Y data
## Removing all columns except the relevant X and Y coordinates

```{r}
setwd('C:\\Research data\\Large_Scale3.RAW\\raw_data_dat')

ALLESFUNCTIE <- function
(.file){
  raw <- read.table(.file, skip=4, sep="")
  raw[,c(8,9)]
}
filenames <- Sys.glob("*.dat")  
RAW_EO_LS3 <- lapply(filenames, ALLESFUNCTIE) # 301 participants * 4 trials = 1204 elements

#save(RAW_EO_LS3, file="RAW_EO_LS3.Rdata")

setwd('C:\\Research data\\Large_Scale3.RAW\\raw_data_dat')
load("RAW_EO_LS3.Rdata")

```


## 1.2 defining names of files

* Extracting name based on file name * 

```{r}

library(tidyverse)
library(segmented)
library(seewave)

setwd('C:\\Research data\\Large_Scale3.RAW\\raw_data_dat')
filenames <- Sys.glob("*.dat")  # extracting file names from directory once again

# Subject name
subj <- str_sub(filenames, 3, 6)
names_split <- strsplit(subj, split='_', fixed=TRUE)
Subj <- unlist(names_split)

# Trial 1-2-3-4
onetofour <- 1:4
trialnum <- vector()
for(i in 1:301){
  trialnum <- c(trialnum, onetofour)
}

# Combining both
names <- paste(Subj, trialnum, sep="_")


```

1.3 Converting data into lagged

```{r}
setwd('C:\\Research data\\Large_Scale3.RAW\\raw_data_dat')
load("RAW_EO_LS3.Rdata")

# Creating empty lists

list_lagged_distances_X <- list()
list_lagged_distances_Y <- list()
list_lagged_distances_R <- list()

# First test on a smaller sample! later, replace test with tot

test <- 1
tot <- 1204

ptm <- proc.time()

for(l in 1:tot){

data <- RAW_EO_LS3[[l]]

# Create extra second at the beginning and at the end
extra1 <- data[c(1000:1),]
extra2 <- data[c(30000:29001),]

data <- rbind.data.frame(extra1, data, extra2)

# We make this "fake" points because butterworse filter will distort the first and last data points.

# Butterworse filtering
f=1000
data$V8 <- bwfilter(data$V8, f=f, n=4, to=13)
data$V9 <- bwfilter(data$V9, f=f, n=4, to=13)

ROW <- nrow(data)
data <- data[c(1001:(ROW-1000)),] # Removing "fake" points after filter application

colnames(data) <- c("X", "Y")

# Downsampling

#data = data[seq(1, nrow(data), 10), ]

# Don't downsample in eventual data

# Actual calculation

## Max lag 10 seconds
Maxlag = 10000

total_points <- nrow(data$X)

diffusion_analysis_X <- vector()
diffusion_analysis_Y <- vector()
diffusion_analysis_R <- vector()

for(i in 1:Maxlag){
  
  X1 <- data[seq(1, (total_points-i), 1),]
  X2 <- data[seq((1+i), total_points, 1),]
  
  lags <- X1-X2
  
  diffusion_analysis_X[i] <- mean(lags$X^2)
  diffusion_analysis_Y[i] <- mean(lags$Y^2)
  diffusion_analysis_R[i] <- mean(lags$X^2+lags$Y^2)
  
}


time <- 1:10000

lagged_distances_X <- cbind.data.frame(time, diffusion_analysis_X)
lagged_distances_Y <- cbind.data.frame(time, diffusion_analysis_Y)
lagged_distances_R <- cbind.data.frame(time, diffusion_analysis_R)

colnames(lagged_distances_X) <- c("time","results")
colnames(lagged_distances_Y) <- c("time","results")
colnames(lagged_distances_R) <- c("time","results")


list_lagged_distances_X[[l]] <- lagged_distances_X
list_lagged_distances_Y[[l]] <- lagged_distances_Y
list_lagged_distances_R[[l]] <- lagged_distances_R

}



names(list_lagged_distances_X) <- names
names(list_lagged_distances_Y) <- names
names(list_lagged_distances_R) <- names

list_lagged_distances_EO_X <- list_lagged_distances_X

list_lagged_distances_EO_Y <- list_lagged_distances_Y

list_lagged_distances_EO_R <- list_lagged_distances_R



setwd('C:\\Research data\\Large_Scale3.RAW\\raw_data_dat')
save(list_lagged_distances_EO_X, file="list_lagged_distances_EO_X.Rdata")
save(list_lagged_distances_EO_Y, file="list_lagged_distances_EO_Y.Rdata")
save(list_lagged_distances_EO_R, file="list_lagged_distances_EO_R.Rdata")

proc.time() - ptm

```




# 2. Eyes closed 
## 2.1 Selecting X and Y data
```{r}


setwd('C:\\Research data\\Large_Scale3.RAW\\raw_data_ec_dat')

ALLESFUNCTIE <- function
(.file){
  
  raw <- read.table(.file, skip=4, sep="")
  raw[,c(8,9)]
  
}
filenames <- Sys.glob("*.dat")  
ALLES <- lapply(filenames, ALLESFUNCTIE)


RAW_EC_LS3 <- ALLES

save(RAW_EC_LS3, file="RAW_EC_LS3.Rdata")


```

## 2.2 defining names of files
```{r}
setwd('C:\\Research data\\Large_Scale3.RAW\\raw_data_ec_dat')
filenames <- Sys.glob("*.dat")  # however you get the list of file  # !! DAT of dat is een verschil !! 

subj <- str_sub(filenames, 3, 6)
names_split <- strsplit(subj, split='_', fixed=TRUE)
Subj <- unlist(names_split)

onetofour <- 1:4
names_2 <- vector()
for(i in 1:300){
  names_2 <- c(names_2, onetofour)
}

names <- paste(Subj, names_2, sep="_")

```

1.3 Converting data into lagged

```{r}
setwd('C:\\Research data\\Large_Scale3.RAW\\raw_data_ec_dat')


load("RAW_EC_LS3.Rdata")

### test op NR 1

list_lagged_distances_X <- list()
list_lagged_distances_Y <- list()
list_lagged_distances_R <- list()

lengthdata <- length(filenames)

test <- 24
tot <- lengthdata

ptm <- proc.time()

for(l in 1:tot){

data <- RAW_EC_LS3[[l]]

# Create extra second at the beginning and at the end
extra1 <- data[c(1000:1),]
extra2 <- data[c(30000:29001),]

data <- rbind.data.frame(extra1, data, extra2)

# We make this "fake" points because butterworse filter will distort the first and last data points.

# Butterworse filtering
f=1000
data$V8 <- bwfilter(data$V8, f=f, n=4, to=13)
data$V9 <- bwfilter(data$V9, f=f, n=4, to=13)

ROW <- nrow(data)
data <- data[c(1001:(ROW-1000)),] # Removing "fake" points after filter application

colnames(data) <- c("X", "Y")

# Downsampling

#data = data[seq(1, nrow(data), 10), ]

# Don't downsample in eventual data

# Actual calculation


## Max lag 10 seconds
Maxlag = 10000

total_points <- nrow(data$X)

diffusion_analysis_X <- vector()
diffusion_analysis_Y <- vector()
diffusion_analysis_R <- vector()

for(i in 1:Maxlag){
  
  X1 <- data[seq(1, (total_points-i), 1),]
  X2 <- data[seq((1+i), total_points, 1),]
  
  lags <- X1-X2
  
  diffusion_analysis_X[i] <- mean(lags$X^2)
  diffusion_analysis_Y[i] <- mean(lags$Y^2)
  diffusion_analysis_R[i] <- mean(lags$X^2+lags$Y^2)
  
}


time <- 1:10000

lagged_distances_X <- cbind.data.frame(time, diffusion_analysis_X)
lagged_distances_Y <- cbind.data.frame(time, diffusion_analysis_Y)
lagged_distances_R <- cbind.data.frame(time, diffusion_analysis_R)

colnames(lagged_distances_X) <- c("time","results")
colnames(lagged_distances_Y) <- c("time","results")
colnames(lagged_distances_R) <- c("time","results")


list_lagged_distances_X[[l]] <- lagged_distances_X
list_lagged_distances_Y[[l]] <- lagged_distances_Y
list_lagged_distances_R[[l]] <- lagged_distances_R

}


names(list_lagged_distances_X) <- Subj
names(list_lagged_distances_Y) <- Subj
names(list_lagged_distances_R) <- Subj

list_lagged_distances_EC_X <- list_lagged_distances_X

list_lagged_distances_EC_Y <- list_lagged_distances_Y

list_lagged_distances_EC_R <- list_lagged_distances_R


save(list_lagged_distances_EC_X, file="list_lagged_distances_EC_X.Rdata")
save(list_lagged_distances_EC_Y, file="list_lagged_distances_EC_Y.Rdata")
save(list_lagged_distances_EC_R, file="list_lagged_distances_EC_R.Rdata")

proc.time() - ptm

```



# 3. Tandem
## 3.1 Selecting X and Y data
```{r}


setwd('C:\\Research data\\Large_Scale3.RAW\\raw_data_romberg_dat')

ALLESFUNCTIE <- function
(.file){
  
  raw <- read.table(.file, skip=4, sep="")
  raw[,c(8,9)]
  
}
filenames <- Sys.glob("*.dat")  # however you get the list of file  # !! DAT of dat is een verschil !! 
ALLES <- lapply(filenames, ALLESFUNCTIE)


RAW_TR_LS3 <- ALLES

save(RAW_TR_LS3, file="RAW_TR_LS3.Rdata")


```

## 2.2 defining names of files
```{r}
setwd('C:\\Research data\\Large_Scale3.RAW\\raw_data_romberg_dat')
filenames <- Sys.glob("*.dat")  # however you get the list of file  # !! DAT of dat is een verschil !! 

subj <- str_sub(filenames, 3, 6)
names_split <- strsplit(subj, split='_', fixed=TRUE)
Subj <- unlist(names_split)

onetofour <- 1:4
names_2 <- vector()
for(i in 1:300){
  names_2 <- c(names_2, onetofour)
}

names <- paste(Subj, names_2, sep="_")

```

1.3 Converting data into lagged

```{r}
setwd('C:\\Research data\\Large_Scale3.RAW\\raw_data_romberg_dat')


load("RAW_TR_LS3.Rdata")

### test op NR 1

list_lagged_distances_X <- list()
list_lagged_distances_Y <- list()
list_lagged_distances_R <- list()

lengthdata <- length(filenames)

test <- 24
tot <- lengthdata

ptm <- proc.time()

for(l in 1:tot){

data <- RAW_TR_LS3[[l]]

# Create extra second at the beginning and at the end
extra1 <- data[c(1000:1),]
extra2 <- data[c(30000:29001),]

data <- rbind.data.frame(extra1, data, extra2)

# We make this "fake" points because butterworse filter will distort the first and last data points.

# Butterworse filtering
f=1000
data$V8 <- bwfilter(data$V8, f=f, n=4, to=13)
data$V9 <- bwfilter(data$V9, f=f, n=4, to=13)

ROW <- nrow(data)
data <- data[c(1001:(ROW-1000)),] # Removing "fake" points after filter application

colnames(data) <- c("X", "Y")

# Downsampling

#data = data[seq(1, nrow(data), 10), ]

# Don't downsample in eventual data

# Actual calculation


## Max lag 10 seconds
Maxlag = 10000

total_points <- nrow(data$X)

diffusion_analysis_X <- vector()
diffusion_analysis_Y <- vector()
diffusion_analysis_R <- vector()

for(i in 1:Maxlag){
  
  X1 <- data[seq(1, (total_points-i), 1),]
  X2 <- data[seq((1+i), total_points, 1),]
  
  lags <- X1-X2
  
  diffusion_analysis_X[i] <- mean(lags$X^2)
  diffusion_analysis_Y[i] <- mean(lags$Y^2)
  diffusion_analysis_R[i] <- mean(lags$X^2+lags$Y^2)
  
}


time <- 1:10000

lagged_distances_X <- cbind.data.frame(time, diffusion_analysis_X)
lagged_distances_Y <- cbind.data.frame(time, diffusion_analysis_Y)
lagged_distances_R <- cbind.data.frame(time, diffusion_analysis_R)

colnames(lagged_distances_X) <- c("time","results")
colnames(lagged_distances_Y) <- c("time","results")
colnames(lagged_distances_R) <- c("time","results")


list_lagged_distances_X[[l]] <- lagged_distances_X
list_lagged_distances_Y[[l]] <- lagged_distances_Y
list_lagged_distances_R[[l]] <- lagged_distances_R

}


names(list_lagged_distances_X) <- Subj
names(list_lagged_distances_Y) <- Subj
names(list_lagged_distances_R) <- Subj

list_lagged_distances_TR_X <- list_lagged_distances_X

list_lagged_distances_TR_Y <- list_lagged_distances_Y

list_lagged_distances_TR_R <- list_lagged_distances_R


save(list_lagged_distances_TR_X, file="list_lagged_distances_TR_X.Rdata")
save(list_lagged_distances_TR_Y, file="list_lagged_distances_TR_Y.Rdata")
save(list_lagged_distances_TR_R, file="list_lagged_distances_TR_R.Rdata")

proc.time() - ptm

```

